A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-05-19 paper/paper.tex
Added another downarrow

What about our relationship to the $k{\downarrow}$ of
\citet{UpcomingAAAIPaper}?  \Cref{figure:prettyheatmaps3} plots the number of
recursive calls made by $k{\downarrow}$ and \McSplit{$\downarrow$} on each of the subgraph
isomorphism instances. Although \McSplit{$\downarrow$} is the faster of the two algorithms overall, it
explores more search nodes than $k{\downarrow}$ for most instances (even taking
into account that $k{\downarrow}$ uses a unit propagation loop, and so measures
the search tree slightly differently). This is the classic tradeoff between
speed and cleverness. A hybrid algorithm could be beneficial here: it could use
$k{\downarrow}$ initially, switching to \McSplit\ when the extra filtering is
ineffective, and finally switching to a clique encoding when fewer than some
threshold number of vertices remain to be selected. This might deliver the
benefits of the clique encoding for labelled graphs, while avoiding the high
memory cost and colouring time of encoding the full instance.

>>>>

What about our relationship to the $k{\downarrow}$ of
\citet{UpcomingAAAIPaper}?  \Cref{figure:prettyheatmaps3} plots the number of
recursive calls made by $k{\downarrow}$ and \McSplit{$\downarrow$} on each of the subgraph
isomorphism instances. Although \McSplit{$\downarrow$} is the faster of the two algorithms overall, it
explores more search nodes than $k{\downarrow}$ for most instances (even taking
into account that $k{\downarrow}$ uses a unit propagation loop, and so measures
the search tree slightly differently). This is the classic tradeoff between
speed and cleverness. A hybrid algorithm could be beneficial here: it could use
$k{\downarrow}$ initially, switching to \McSplit{$\downarrow$} when the extra filtering is
ineffective, and finally switching to a clique encoding when fewer than some
threshold number of vertices remain to be selected. This might deliver the
benefits of the clique encoding for labelled graphs, while avoiding the high
memory cost and colouring time of encoding the full instance.
